### 2019-04-03 papers/journal/encoding.tex
Updated Pairing encoding for the SMT

\subsubsection{Constraints on presence, activity of the molecule, and pairing matrix}
%
We need the following constraints \texttt{EdgeC},
\texttt{ActivityC} and \texttt{PairingC} to encode the basic structure of VTSs.
%
For an edge to exist it should have one molecule present. 
%
\begin{align*}
  \texttt{PresentE} = \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
\end{align*}
The edge labels are subset of the node labels of the source and target nodes.
\begin{align*}
  \texttt{LabelE} = \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
\end{align*}
Self edges are not allowed. 
\begin{align*}
  \texttt{SelfE} = \bigwedge\limits_{i,q} \neg e_{i,i,q}
\end{align*}
\noindent We define \texttt{EdgeC} to collect all the edge related constraints. 
%
\texttt{EdgeC} states that each edge has at least one molecule,
 edge labels are consistent with node labels and there are no self loops.    
\begin{align*}
  \texttt{EdgeC} = \texttt{PresentE} \land \texttt{LabelE}  \land \texttt{SelfE} 
\end{align*}
\noindent If a molecule is active on an edge, it should be present on the edge.
%
\begin{align*}
  \texttt{ActiveMolE} = \bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies e_{i,j,q,m}\label{eq:f1}
\end{align*}
A molecule should be present to be active on a node.  
\begin{align*}
    \texttt{ActiveMolN} = \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
\end{align*}
\noindent We define \texttt{ActivityC} to collect all the molecule activity related constraints. 
\texttt{ActivityC} states that all active molecules are present.
\begin{align*}
  \texttt{ActivityC} = \texttt{ActiveMolE} \land \texttt{ActiveMolN} 
\end{align*}
\noindent We divide the pairing matrix into Q-SNAREs and R-SNAREs blocks and set the dependency bits of Q-SNAREs to Q-SNAREs and R-SNAREs to R-SNAREs in the pairing matrix to be all 0's.
%It reduces the search space.
% Condition on $p_{kk'}$. \ashu{why???} .
%\begin{align}
%  \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y)
%  \tag{V6}\label{eq:c3}
%\end{align}

\begin{align*}
 \texttt{PairingC} =\;& \bigwedge\limits_{(x < 3M/4 \, \land  \, y < 3M/4) \lor  (x >= 3M/4 \, \land \, y >= 3M/4)} \neg p(x,y)
\end{align*}

>>>>

\subsubsection{Constraints on presence, activity of the molecule, and pairing matrix}
%
We need the following constraints \texttt{EdgeC},
\texttt{ActivityC} and \texttt{PairingC} to encode the basic structure of VTSs.
%
For an edge to exist it should have one molecule present. 
%
\begin{align*}
  \texttt{PresentE} = \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
\end{align*}
The edge labels are subset of the node labels of the source and target nodes.
\begin{align*}
  \texttt{LabelE} = \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
\end{align*}
Self edges are not allowed. 
\begin{align*}
  \texttt{SelfE} = \bigwedge\limits_{i,q} \neg e_{i,i,q}
\end{align*}
\noindent We define \texttt{EdgeC} to collect all the edge related constraints. 
%
\texttt{EdgeC} states that each edge has at least one molecule,
 edge labels are consistent with node labels and there are no self loops.    
\begin{align*}
  \texttt{EdgeC} = \texttt{PresentE} \land \texttt{LabelE}  \land \texttt{SelfE} 
\end{align*}
\noindent If a molecule is active on an edge, it should be present on the edge.
%
\begin{align*}
  \texttt{ActiveMolE} = \bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies e_{i,j,q,m}\label{eq:f1}
\end{align*}
A molecule should be present to be active on a node.  
\begin{align*}
    \texttt{ActiveMolN} = \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
\end{align*}
\noindent We define \texttt{ActivityC} to collect all the molecule activity related constraints. 
\texttt{ActivityC} states that all active molecules are present.
\begin{align*}
  \texttt{ActivityC} = \texttt{ActiveMolE} \land \texttt{ActiveMolN} 
\end{align*}
\noindent We divide the pairing matrix into Q-SNAREs and R-SNAREs blocks and set the dependency bits of R-SNAREs to R-SNAREs in the pairing matrix to be all 0's.
%It reduces the search space.
% Condition on $p_{kk'}$. \ashu{why???} .
%\begin{align}
%  \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y)
%  \tag{V6}\label{eq:c3}
%\end{align}

\begin{align*}
 \texttt{PairingC} =\;& \bigwedge\limits_{(x >= 3M/4 \, \land \, y >= 3M/4)} \neg p(x,y)
\end{align*}
